Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-10 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
one of the acronyms

The main problem with Java and all the other browser-embedded
technologies is that they are not {\em universal} in the
sense that an extra component, namely, the Java virtual machine or another
virtual environment has to be installed in the browser.
Also these virtual environments have become targets of malicious attacks; 
for instance numerous vulnerabilities have been discovered in 
the proprietary Adobe Flash runtime environment and
video player \cite{ford2009analyzing,watanabe2010new}. The need for
these additional environments has been mitigated with the
adoption of the HTML5 standard \cite{anthes2012html5}.
JavaScript \cite{flanagan2006javascript}, however, has become a set of standards
\cite{ECMA-262} that include the language and its components. Since
early on, it was adopted by the industry and also by scientists,
who used them for creating an EA on
the browser as early as 1998 \cite{jj-ppsn98}.

>>>>

The main problem with Java and all the other browser-embedded
technologies is that they are not {\em universal} in the
sense that an extra component, namely, the Java virtual machine or another
virtual environment has to be installed in the browser.
Also these virtual environments have become targets of malicious attacks; 
for instance numerous vulnerabilities have been discovered in 
the proprietary Adobe Flash runtime environment and
video player \cite{ford2009analyzing,watanabe2010new}. The need for
these additional environments has been mitigated with the
adoption of the HTML5 standard \cite{anthes2012html5}.
JavaScript \cite{flanagan2006javascript}, however, has become a set of standards
\cite{ECMA-262} that include the language and its components. Since
early on, it was adopted by the industry and also by scientists,
who used them for creating an evolutionary algorithm (EA) on
the browser as early as 1998 \cite{jj-ppsn98}.
